---
output: md_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup_rmd, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

[![DOI](https://sandbox.zenodo.org/badge/1337052177.svg)](https://handle.test.datacite.org/10.5072/zenodo.588641)


# A Nonparametric Phase II Monitoring Framework for Functional Data via Mahalanobis Distances

The goal of this repository is to provide reproducible code for the methods and case studies on the paper "A Nonparametric Phase II Monitoring Framework for Functional Data via Mahalanobis Distances" by Priscila Guayasamín, Miguel Flores, Emilio L. Cano, Javier M. Moguerza, Javier Tarrío‐Saavedra, and Salvador Naya, submitted to the journal *Quality and Reliability Engineering International*.

This readme file follows the structure of the paper, and it is divided into sections that correspond to the sections of the paper. Each section contains a brief description of the methods and case studies, as well as links to the corresponding code and data.

## Environment setup

In order to reproduce the results of the paper, you can clone this repository and open it with your preferred IDE, e.g., RStudio, Positron, or even a terminal window and the R console.

This repository is configured to use the [{renv}](https://rstudio.github.io/renv/) package to manage dependencies. To install the required packages, you can run the following code in your R console:

```{r setup_renv, eval = FALSE}
renv::restore()
```

Please note that you need the {renv} package installed to use this functionality.

Optionally, you can manually install the required packages, but complete reproducibility is only guaranteed when using the same package versions as those used in the paper. The required packages are the following (note that one of them is not available on CRAN and must be installed from github, for example using the {pak} package):

* {extrafont}
* {extrafont}
* {data.table}
* {fda.usc}
* {qcr}
* {imputeTS}
* {fdahotelling}, not in CRAN: <https://github.com/astamm/fdahotelling>
* {ggplot2}
* {readxl}
* {janitor}
* {dplyr}
* {tidyr}
* {parallel}
* {doSNOW}
* {doRNG}
* {patchwork}

The `sessionInfo()` output at the end of this file contains the versions of the loaded packages used in the last update of this repository.

The script `R/000_setup.R` contains the code to setup the environment and load the required packages. You can run it with the following code:

```{r setup_r, eval = FALSE}
source("R/000_setup.R")
```

In addition to loading the packages, the script also creates the `params` object, a list that contains the parameters used throughout the code. You can modify the parameters in this list to change the behavior of the code. Furthermore, the helper functions in `R/001_helper_functions.R` are loaded to provide additional functionality. Some other expressions are run to configure input and output options.


## Simulations

The simulations scripts are located at `R/simulations`. There is a folder for each scenario, and within each folder there are scripts for each simulation setting. The results of the simulations are saved in the `results/simulations` folder. The script `R/simulations/000_setup_sim.R` contains the code to setup the simulations, including the parameters and the parallelization setup. The scripts for each simulation setting are named according to the following pattern: `<stat>_<method>_<n1>_<n2>_<scenario>.R`, where `<stat>` is the statistic used, `<method>` is the method used, `<n1>` is the calibration sample size, `<n2>` is the monitoring sample size, and `<scenario>` is the scenario code.

Before running the individual simulation scripts, you can run the `R/simulations/000_setup_sim.R` script to setup the environment and load the required packages. You can run it with the following code:

```{r setup_sim, eval = FALSE}
source("R/simulations/000_setup_sim.R")
```

Then, the simulation scripts can be run in order, or you can run them individually. The results of the simulations are saved in the `results/simulations` folder, and they can be loaded with the `load()` function. The results are saved as RData files, and they contain the objects `senal` and `potencia`, which correspond to the out-of-control signal and the power of the test, respectively.


**NOTE**: Even though the simulations are paralelized, they may take a long time to run, depending on the number of simulations and the computational resources available. You can modify the parameters in the `R/simulations/000_setup_sim.R` object to change the number of simulations, the number of bootstrap samples, and the sample sizes.

The following expression can be used to run all the simulations in order:

```{r run_simulations, eval = FALSE}
source("R/simulations/000_setup_sim.R")
for (f in list.files("R/simulations/Scenario1A", pattern = "\\.R$", full.names = TRUE)) {
  source(f)
}
for (f in list.files("R/simulations/Scenario1B", pattern = "\\.R$", full.names = TRUE)) {
  source(f)
}
for (f in list.files("R/simulations/Scenario2A", pattern = "\\.R$", full.names = TRUE)) {
  source(f)
}
for (f in list.files("R/simulations/Scenario2B", pattern = "\\.R$", full.names = TRUE)) {
  source(f)
}
```

The results of each simulation can be visualized by loading the objects and showing the results. For example, to visualize the results of the simulation `l1std_bootstrap_150_100_1A.R`, you can run the following code:

```{r visualize_results_sim, eval = FALSE}
load("results/simulations/l1std_boot_100_50_1A.RData")
print(potencia_l1std_boot_100_50)
print(mean(senal_l1std_boot_100_50[[1]]))
```

**NOTE**: The results may not be exactly the same as those reported in the paper, since the simulations are based on random samples that can vary across R versions and hardware architectures. However, they should be very similar, and the conclusions should be the same.

## Case study 1: Monitoring of NO<sub>2</sub> concentration in Madrid (COVID-19 lockdown)

The original data for this case study is available in the `data/case_study_2` folder. The code to reproduce the results of this case study is available in the `R/case_study_2` folder. The script `R/case_study_2/000_data_prep.R` prepares the data, whereas `R/case_study_2/001_case_study_2_phaseI.R` and `R/case_study_2/002_case_study_2_phaseII_monitoring.R` run the Phase I and Phase II monitoring respectively. The results are saved in the `results/case_study_2` folder. Thus, you can open and run the code of the scripts line by line to check all the intermediate results, or run the following code to run the scripts in order:

```{r run_case_study_1, eval = FALSE}
source("R/case_study_1/000_data_prep.R")
source("R/case_study_1/001_case_study_1_phaseI_paired.R")
source("R/case_study_1/002_case_study_1_phaseII_monitoring_paired.R")
```



## Case study 2: Monitoring electricity consumption in a retail store (Panama City)

The original data for this case study is available in the `data/case_study_1` folder. The code to reproduce the results of this case study is available in the `R/case_study_1` folder. The script `R/case_study_1/000_data_prep.R` prepares the data, whereas `R/case_study_1/001_case_study_1_phaseI_paired.R` and `R/case_study_1/002_case_study_1_phaseII_monitoring_paired.R` run the Phase I and Phase II monitoring respectively. The results are saved in the `results/case_study_1` folder. Thus, you can open and run the code of the scripts line by line to check all the intermediate results, or run the following code to run the scripts in order:

```{r run_case_study_2, eval = FALSE}
source("R/case_study_2/000_data_prep.R")
source("R/case_study_2/001_case_study_2_phaseI.R")
source("R/case_study_2/002_case_study_2_phaseII_monitoring.R")
```

## ARL experiment

The code for the ARL experiment in the conclusions can be found in the script `R/ARL/ARL_simulations.R`. It contains helper functions, data generation, simulations, and ARL computations. The results are saved in the `results/ARL_experiment` folder. The code can be run line by line from the script to see the intermediate results, or all at once with the following expression:

```{r arl_experiment, eval = FALSE}
source("R/ARL/ARL_simulations.R")
```


# Session Info

The following code chunk prints out the session information corresponding to the last repository update, which is useful for reproducibility.

```{r session_info, echo = TRUE}
sessionInfo()
```

Run this code to update the README.md file from README.Rmd, if needed:

```{r update_readme, eval = FALSE}
rmarkdown::render("README.Rmd", output_format = "md_document")
```
